Draft for project

### 2014-10-31 draft_project.tex
Er det fiksa, er det lov å spørre seg.

	\item[Convergence of $u_{n_j}$:] Since all $u_{n_j}$ are classical solutions, they're also weak solutions. Therefore, when putting $u_{n_j}$ and $u_{n_k}$ into (\ref{weak}) and taking their difference, 
	\begin{align*}
	-\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt &= -\iint_{Q_T}\nabla(w_{n_j} - w_{n_k})\cdot \nabla \eta dxdt \\
	&+ \int_\Omega (u_{0,n_j} - u_{0,n_k})\eta\big|_{t=0}dx \\
	&+ \iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt 
	\end{align*}	 
	pops out. Restricting ourselves to only $\eta \in C^\infty_c(Q_T)$, and doing integration by parts on the term involving $w$, yields
	\begin{equation*}
	\bigg|\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt \bigg| \leq \bigg|\iint_{Q_T} (w_{n_j} - w_{n_k})\Delta\eta dxdt \bigg| +  \bigg|\iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt\bigg|,
	\end{equation*}
	where the term concerning the initial data has dropped out following that $\eta \big|_{t=0} = 0$. The first and the last term can both be made arbitrarily small by the convergence of $w_{n_j}$ and $f_n$ respectively. And so $\partial_t u_{n_j}$ in the weak sense is a Cauchy sequence in $L^1_{loc}(Q_T)$, and since $Q_T$ is bounded, also in $L^1(Q_T)$.

	\item[Showing that $w=\Phi(u)$:] It is sensible to break this part into two similar steps. First, fix $k \in \mathbb{N}$ and consider the sequence $\Phi_n(u_k)$, which converges points wise to $\Phi(u_k)$. Let now $\psi$ be a function in $L^1(Q_T)$ with compact support. We want to show that
	\begin{equation*}
	\iint_{Q_T} \Phi_n(u_k) \psi dxdt \to \iint_{Q_T}\Phi(u_k)\psi dxdt.
	\end{equation*}
	This is accomplished using the Dominated Convergence Theorem (DCT). So we note that since $|u_k| \leq C$, 
	\begin{align*}
    |\Phi_n(u_k)| &\leq \int_\mathbb{R} \left| \Phi(u_k-y) + \frac{u_k-y}{n}\right|\eta_{\frac{1}{n}}(y)dy \\
    &\leq \underset{|s|\leq C+1/n}{sup}\left| \Phi(s) + \frac{s}{n}\right| < \infty,
	\end{align*}
	due to the support of $\eta_{\frac{1}{n}}$ being contained in $\left[ -\frac{1}{n}, \frac{1}{n}\right]$. Thus we set $M = \mathrm{sup}_{|s|\leq C+1}\left|\Phi(s) + s\right|$. Then $|\Phi_n(u_k)\psi| \leq M|\psi| \in L^1(Q_T)$, and we can use the DCT to establish that the proposed limit holds.

@@

@@

\end{appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliographystyle{plainnat}
\bibliography{project_bibliography.bib}
\end{document}

>>>>

	\item[Convergence of $u_{n_j}$:] Since all $u_{n_j}$ are classical solutions, they're also weak solutions. Therefore, when putting $u_{n_j}$ and $u_{n_k}$ into (\ref{weak}) and taking their difference, 
	\begin{align*}
	-\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt &= -\iint_{Q_T}\nabla(w_{n_j} - w_{n_k})\cdot \nabla \eta dxdt \\
	&+ \int_\Omega (u_{0,n_j} - u_{0,n_k})\eta\big|_{t=0}dx \\
	&+ \iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt 
	\end{align*}	 
	pops out. Restricting ourselves to only $\eta \in C^\infty(Q_T)$ that vanish on $\partial \Omega \times [0,T]$ and for $t=T$, and doing integration by parts on the term involving $w$, yields
	\begin{align*}
	\bigg|\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt \bigg| &\leq \bigg|\iint_{Q_T} (w_{n_j} - w_{n_k})\Delta\eta dxdt \bigg| \\
	&+ \bigg| \int_\Omega (u_{0,n_j} - u_{0,n_k})\eta\big|_{t=0} dx \bigg| \\
	 &+  \bigg|\iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt\bigg|.
	\end{align*}
	 All terms can be made arbitrarily small by the convergences of $w_{n_j}$, $u_{0,n}$ and $f_n$ respectively. And so $\partial_t u_{n_j}$ in the weak sense is a Cauchy sequence in $L^1_{loc}(Q_T)$, and since $Q_T$ is bounded, also in $L^1(Q_T)$. By the completeness of $L^1(Q_T)$, it must also converge. The primitive of this limit is then determined up to a constant independent of $t$. However, the limit is completely determined when taking into account the initial data.

	 To see this we call $v$ the weak time derivative of the limit of $u_{n_j}$, and $g$ its primitive. That is, for every $\eta \in C^\infty_c (Q_T)$ we have
	 \begin{equation*}
	 \iint_{Q_T} g\partial_t\eta dxdt = -\iint_{Q_T}v\eta dxdt.
	 \end{equation*}
	 In addition we impose the condition that
	 \begin{equation*}
	 \lim_{\epsilon \to 0} \iint_{Q_T}g \eta_\epsilon dxdt = \frac{1}{2}\int_\Omega u_0dx,
	 \end{equation*}
	 where $\eta_\epsilon$ is here the standard mollifier with respect to only the temporal dimension. Note that the factor $\frac{1}{2}$ comes from the mollifier being symmetric about the origin and we only integrate over positive values of $t$. With these two conditions $g$ can be uniquely determined. So $u_{n_j}$ converges in $L^1(Q_T)$ and we call the limit $u$.

	\item[Showing that $w=\Phi(u)$:] It is sensible to break this part into two similar steps. First, fix $k \in \mathbb{N}$ and consider the sequence $\Phi_n(u_k)$, which converges pointwise to $\Phi(u_k)$. Let now $\psi$ be a function in $L^1(Q_T)$ with compact support. We want to show that
	\begin{equation*}
	\iint_{Q_T} \Phi_n(u_k) \psi dxdt \to \iint_{Q_T}\Phi(u_k)\psi dxdt.
	\end{equation*}
	This is accomplished using the Dominated Convergence Theorem (DCT). So we note that since $|u_k| \leq C$, 
	\begin{align*}
    |\Phi_n(u_k)| &\leq \int_\mathbb{R} \left| \Phi(u_k-y) + \frac{u_k-y}{n}\right|\eta_{\frac{1}{n}}(y)dy \\
    &\leq \underset{|s|\leq C+1/n}{sup}\left| \Phi(s) + \frac{s}{n}\right| < \infty,
	\end{align*}
	due to the support of $\eta_{\frac{1}{n}}$ being contained in $\left[ -\frac{1}{n}, \frac{1}{n}\right]$. Thus we set $M = \mathrm{sup}_{|s|\leq C+1}\left|\Phi(s) + s\right|$. Then $|\Phi_n(u_k)\psi| \leq M|\psi| \in L^1(Q_T)$, and we can use the DCT to establish that the proposed limit holds.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliographystyle{plainnat}
\bibliography{project_bibliography.bib}

@@

\end{appendix}
\end{document}
